Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis

### 2019-10-16 manuscript/manuscript.Rmd
plot code simplified

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis"
titlerunning: Accuracy of zero-heat-flux temperature monitoring
authorrunning: Conway
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

@@

```{r meta-function, echo=FALSE}
meta <-  function(Te,V_T){
m <- length(Te)
wt_FE=1/V_T
T_FE <- sum(Te*wt_FE)/sum(wt_FE)
Q <- sum(wt_FE*(Te - T_FE)^2)
S1 <- sum(wt_FE)
S2 <- sum(wt_FE^2)
o2 <- (Q - (m - 1))/(S1 - S2/S1)
wt_RE <- 1/(V_T + o2)
T_RE <- sum(Te*wt_RE)/sum(wt_RE)
V_T_RE_mod <- 1/sum(wt_RE)
V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
}
loa_maker <- function(bias,V_bias,logs2,V_logs2) {
bias_row=meta(bias, V_bias)
logs2_row=meta(logs2, V_logs2)
bias_mean <- bias_row[2]
sd2_est <- exp(logs2_row[2])
tau_est <- bias_row[3]
LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
m <- bias_row[1]
tcrit <- qt(1-.05/2,m-1)
B1 <- sd2_est^2/(sd2_est + tau_est)
B2 <- tau_est^2/(sd2_est + tau_est)
wt <- 1/V_bias
S1 <- sum(wt)
S2 <- sum(wt^2)
S3 <- sum(wt^3)
A0 <- 2*(m-1)/(S1-S2/S1)^2
A1 <- 4/(S1 - S2/S1)
A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
}
```

@@

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
library(ggplot2)
  library(tibble)
  library(tidyverse)
  library(ggfittext)

  line_size <- 0.50
  box_type <- "round"
  box_lines <- 0.5
  box_colour <- "#ff4f14"
  box_fill <- "white"
  text_colour <- "#ff4f14"
  arrow_colour <- "#ff4f14"

  retrieved <- 129
  duplicates <- 35
  screened <- retrieved-duplicates
  full_text <- 21
  screen_excluded <- screened-full_text
  included <- 15
  full_text_excluded <- full_text-included
  wrong_intervention <- 4
  wrong_comparator <- 2
  wrong_design <- 1
  awaiting_classification <- 2

# Main flow y coordinates  
  import_y_max <- 100
  import_y_min <- 90
  screen_y_max <- 80
  screen_y_min <- 70
  full_y_max <- 60
  full_y_min <- 50
  included_y_max <- 40
  included_y_min <- 30

# Scondary flow y coordinates  
  duplicates_y_max <- 90
  duplicates_y_min <- 80

  full_excluded_y_min <- 25
  full_excluded_y_max <- 45

  screen_excluded_y_min <- 65
  screen_excluded_y_max <- 75

  awaiting_classification_y_min <- 50
  awaiting_classification_y_max <- 60

# x coordinates  
  main_x_min <- 20
  main_x_max <- 70

  second_x_min <- 75
  second_x_max <- 95

  arrow_x <- 45

  ###Plot space set-up####
  data <- tibble(x= 23:100, y = 23:100)
   data %>% 
    ggplot(aes(x, y)) +
    theme_linedraw() +

  ########## Main box flow ###########

  # import box

  annotation_custom(grob = grid::roundrectGrob(gp = grid::gpar(col = box_colour, fill = box_fill)),
    xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=import_y_max)+
    geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=import_y_min, ymax=100,
                  label= glue::glue(retrieved, ' references identified'), 
                  reflow = TRUE, colour = text_colour) +

# screen box
  annotation_custom(grob = grid::roundrectGrob(gp = 
                    grid::gpar(col = box_colour, fill = box_fill)),
                    xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, 
                    ymax=screen_y_max) +
  geom_fit_text(xmin = main_x_min, xmax=main_x_max, ymin=screen_y_min, ymax=screen_y_max,
           label= glue::glue(screened, ' titles and abstracts screened'), 
           reflow = TRUE, colour = text_colour) +

# full text box
  annotation_custom(grob = grid::roundrectGrob(gp = 
          grid::gpar(col = box_colour, fill = box_fill)),
          xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max) +
  geom_fit_text( xmin = main_x_min, xmax=main_x_max, ymin=full_y_min, ymax=full_y_max,
                 label= glue::glue(full_text, ' full-text articles assessed'), 
                  reflow = TRUE, colour = text_colour) +

# included box 
  annotation_custom(grob = grid::roundrectGrob(gp = 
               grid::gpar(col = box_colour, fill = box_fill)),
               xmin = main_x_min, xmax=main_x_max, 
                    ymin=included_y_min, ymax=included_y_max) +
  geom_fit_text(xmin = main_x_min, xmax=main_x_max, 
                ymin=included_y_min, ymax=included_y_max,
                label= glue::glue(included, ' studies included'), 
                 reflow = TRUE, colour = text_colour) +

######### Secondary flow boxes ############

  annotation_custom(grob = grid::roundrectGrob(gp = 
        grid::gpar(col = box_colour, fill = box_fill)),
        xmin = second_x_min, xmax=second_x_max, 
                    ymin=duplicates_y_min, ymax=duplicates_y_max) +
  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
                ymin=duplicates_y_min, ymax=duplicates_y_max,
                label= glue::glue(duplicates, ' duplicates removed'),
                 reflow = TRUE, colour = text_colour) +

# excluded box 
 annotation_custom(grob = 
                              grid::roundrectGrob(gp = 
                              grid::gpar(col = box_colour, fill = box_fill)),
                            xmin = second_x_min, xmax=second_x_max, 
                    ymin=screen_excluded_y_min, ymax=screen_excluded_y_max) +
  geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
                ymin=screen_excluded_y_min, ymax=screen_excluded_y_max,
                label= glue::glue(screen_excluded, ' studies excluded'),
                 reflow = TRUE, colour = text_colour) +

# awaiting classifications box 
    annotation_custom(grob = 
                        grid::roundrectGrob(gp = 
                                              grid::gpar(col = box_colour, fill = box_fill)),
                      xmin = second_x_min, xmax=second_x_max, 
                      ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max) +
    geom_fit_text(xmin = second_x_min, xmax=second_x_max, 
                  ymin=awaiting_classification_y_min, ymax=awaiting_classification_y_max,
                  label= glue::glue(awaiting_classification, ' studies awaiting classification'),
                  reflow = TRUE, colour = text_colour) +

# full text excluded box 
annotation_custom(grob = 
                             grid::roundrectGrob(gp = 
                            grid::gpar(col = box_colour, fill = box_fill)),
                           xmin = second_x_min, xmax=second_x_max, 
                   ymin=full_excluded_y_min, ymax=full_excluded_y_max) +
 geom_fit_text(xmin = second_x_min, xmax=second_x_max,
                ymin=full_excluded_y_max-7, ymax=full_excluded_y_max,
                label= glue::glue(full_text_excluded, ' studies excluded'),
                 reflow = TRUE, colour = text_colour) +
 geom_fit_text(xmin = second_x_min, xmax=second_x_max,
                ymin=full_excluded_y_max-17, ymax=full_excluded_y_max-7,
                label= glue::glue(wrong_intervention, ' wrong intervention','\n',
                                  wrong_intervention, ' wrong comparator','\n',
                                  wrong_intervention, ' wrong design'),
                 colour = text_colour, grow = TRUE) +

####### Main flow arrows#######

  # Import - screen
 geom_segment(
  x=arrow_x, xend = arrow_x, y = import_y_min, yend = screen_y_max+0.25, 
  size = line_size,  colour = arrow_colour,
  arrow = arrow(length = unit(2, "mm"), type= "closed")) +

# Screen - full text
  geom_segment(
    x=arrow_x, xend=arrow_x, y=screen_y_min, yend=full_y_max+0.25, 
    size = line_size,  colour = arrow_colour,
    arrow = arrow(length = unit(2, "mm"), type= "closed")) +

# Full text - included

  geom_segment(
    x=arrow_x, xend=arrow_x, y=full_y_min, yend=included_y_max+0.25, 
    size = line_size,  colour = arrow_colour,
    arrow = arrow(length = unit(2, "mm"), type= "closed")) +

####Secondary flow arrows########

# Import - duplicates

  geom_curve(
    x = arrow_x, xend = second_x_min, 
    y = duplicates_y_max,  yend = duplicates_y_max-5, linetype = "dashed",
    curvature = 0.1, colour = arrow_colour) +

# Screen - excluded

  geom_curve(
    x = arrow_x, xend = second_x_min, 
    y = screen_y_min,  yend = screen_excluded_y_max-5, linetype = "dashed",
    curvature = 0.1, colour = arrow_colour) +

# Screen - awaiting

    geom_curve(
      x = arrow_x, xend = second_x_min, 
      y = screen_y_min,  yend = awaiting_classification_y_max-5, linetype = "dashed",
      curvature = -0.2, colour = arrow_colour) +

  # Full text - excluded

  geom_curve(
    x = arrow_x, xend = second_x_min, 
    y = full_y_min, yend = full_excluded_y_max-10, linetype = "dashed",
    curvature = -0.2, colour = arrow_colour) +

 theme_void() +
  coord_cartesian(ylim = c(23,100))
```

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis"
titlerunning: Accuracy of zero-heat-flux temperature monitoring
authorrunning: Conway
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

@@

```{r meta-function, echo=FALSE}
meta <-  function(Te,V_T){
m <- length(Te)
wt_FE <- 1/V_T
T_FE <- sum(Te*wt_FE)/sum(wt_FE)
Q <- sum(wt_FE*(Te - T_FE)^2)
S1 <- sum(wt_FE)
S2 <- sum(wt_FE^2)
o2 <- (Q - (m - 1))/(S1 - S2/S1)
wt_RE <- 1/(V_T + o2)
T_RE <- sum(Te*wt_RE)/sum(wt_RE)
V_T_RE_mod <- 1/sum(wt_RE)
V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
}
loa_maker <- function(bias,V_bias,logs2,V_logs2) {
bias_row=meta(bias, V_bias)
logs2_row=meta(logs2, V_logs2)
bias_mean <- bias_row[2]
sd2_est <- exp(logs2_row[2])
tau_est <- bias_row[3]
LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
m <- bias_row[1]
tcrit <- qt(1-.05/2,m-1)
B1 <- sd2_est^2/(sd2_est + tau_est)
B2 <- tau_est^2/(sd2_est + tau_est)
wt <- 1/V_bias
S1 <- sum(wt)
S2 <- sum(wt^2)
S3 <- sum(wt^3)
A0 <- 2*(m-1)/(S1-S2/S1)^2
A1 <- 4/(S1 - S2/S1)
A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
}
```

@@

```{r fig-1, fig.align="center", fig.cap="PRISMA Flow Diagram", echo=FALSE, fig.width=5.5, fig.path=""}
# https://github.com/awconway/ggprisma
ggprisma::ggprisma(retrieved = 129, included = 15, duplicates = 35, full_text = 21, wrong_intervention = 4, wrong_comparator = 2, wrong_design = 1, awaiting_classification = 2)
```
